Strings methods analysis

### 2022-08-19 article.tex
parameter setting example removed
introduction simplified

    An important factor for any method will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter. We will also investigate the accuracy of these estimates, since there is no absolutely accurate method for estimating this parameter in a reasonable amount of time.

@@

    Also an important parameter for methods (in this case string methods) is their running time, so this article also considers this parameter. An interesting question is: will mutable or immutable structures be considered? Since this is a complex analysis, both are considered. And also the regularities in the interrelation of mutable and nonmutable methods asymptotics are revealed.

@@

    As an example, consider the following criterion: a method cannot be implemented through three or less methods existing in the set, so that its asymptotics is not degraded.

>>>>

    An important factor for any method will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter.

@@

    Also an important parameter for methods (in this case string methods) is their running time, so this article also considers this parameter. Since this is a complex analysis, the asymptotics of mutable and immutable string functions will be analyzed, as well as the asymptotics under full language immutability.

@@
